\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-24 paper/experiments.tex
Update perf summary
Update perf discussion

%\todobox{actually run experiments and rewrite this section}{
All experiments were run on a single Amazon Web Services EC2 {\tt c4.xlarge} instance, with
four 2.9 GHz Intel Xeon E5-2666 v3 virtual CPUs and 7.5 GiB of main memory, on Debian Linux.

Figure~\ref{fig:runtimes} provides a summary of the performance results. The first plot
shows average running times for \ProjectName{} plans in two configurations:
quality-optimized and runtime-optimized. The second plot shows, for comparison, the average
running times required for each query when performing imputation at the base tables.  In all
cases, running a query through \ProjectName{} is cheaper than imputing a single base table,
with the added advantage of imputation tailored to the query. This latter point adds
significant flexibility to the user, who no longer needs to decide apriori what imputation
strategy they have to stick to for all their queries.

@@

%TODO MJS
Figure~\ref{fig:plantimes} provides a summary of the planning times for each of the queries.
We exclude the planning time for queries that impute at base table, as that requires no
planning. On average, planning constituted 38 percent of total runtime for plans generated
by \ProjectName{}.

@@

Table~\ref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error (SMAPE) for
\ProjectName{}'s query results when compared to running imputation on the base tables and
executing the query on the
cleaned data. Each query was run 10 %TODO MJS
iterations in both settings and then results from the two approaches were paired up and
compared tuple-wise. We average tuple-wise absolute percentage deviations within each
iteration of a query, and we report this value averaged over all iterations.  We can see
that optimizing for quality indeed reduces the SMAPE of query results. In general, the SMAPE
relative to the base-imputation approach are low in all cases, indicating that on-the-fly
imputation produces similar results to imputation at the base tables.

\begin{table}
\centering
\input{perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$ parameterizations relative to results when imputing on base table}
\label{table:smape}
\end{table}

>>>>

All experiments were run on a single Amazon Web Services EC2 {\tt c4.xlarge} instance, with
four 2.9 GHz Intel Xeon E5-2666 v3 virtual CPUs and 7.5 GiB of main memory, on Debian Linux.

Figure~\ref{fig:runtimes} provides a summary of the performance results. The first plot
shows average running times for \ProjectName{} plans in two configurations:
quality-optimized and runtime-optimized. The second plot shows, for comparison, the average
running times required for each query when performing imputation at the base tables.  In all
cases, running a query through \ProjectName{} is cheaper than imputing a single base table,
with performance improvement on a factor of ten.

@@

Figure~\ref{fig:plantimes} provides a summary of the planning times for each of the queries.
We exclude the planning time for queries that impute at base table, as that requires no
planning. In the median query across a variety of queries and choices of $\alpha$, planning
constituted 8.5 percent of total runtime by \ProjectName{}.

@@

Table~\ref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error (SMAPE) for
\ProjectName{}'s query results when compared to running imputation on the base tables and
executing the query on the cleaned data. Each query was run 200 iterations in both settings
and then results from the two approaches were paired up and compared tuple-wise. We average
tuple-wise absolute percentage deviations within each iteration of a query, and we report
this value averaged over all iterations.  We can see that optimizing for quality indeed
reduces the SMAPE of query results. In general, the SMAPE relative to the base-imputation
approach are low in all cases, indicating that on-the-fly imputation produces similar
results to imputation at the base tables.

\begin{table}
\centering
\input{tables/perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$
    parameterizations relative to results when imputing on base table. Values of $0.0$,
    $100.0$, or $NaN$ indicate uninformative values.} %TODO MJS
\label{table:smape}
\end{table}
